\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-02 draft.tex
add more intuition on uncertainty to intro

The fact that \textit{zero} contributions are predicted in equilibrium is not particularly satisfying. The addition of political uncertainty provides the missing realism, smooths the results and delivers additional intuition. I assume all actors are uncertain about the weight the median legislator in a non-unitary legislature places on the profits of the lobbying industry and that this is attributable to the complexity of the legislative process; say, for instance, because a small number of lobbied legislators cannot deliver the votes of their non-lobbied colleagues with certainty. In this case, I show that the legislatures disrupt trade agreements with a higher probability and set higher trade war tariffs when lobbying effort increases. Because the lobbies respond to higher trade agreement tariffs by decreasing effort (and therefore the probability the agreement will fail to be ratified or will be broken), the executives must trade off the level of social welfare derived while a trade agreement is in force---since they prefer low tariffs---and the chances that the agreement will remain in force.

>>>>

The fact that \textit{zero} contributions are predicted in equilibrium is not particularly satisfying. The addition of political uncertainty provides the missing realism, smooths the results and delivers additional intuition. I assume all actors are uncertain about the weight the median legislator in a non-unitary legislature places on the profits of the lobbying industry. \textbf{This is meant to represent the idea that the lobbying and voting ``game'' that goes on within legislatures is often complex enough that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. For instance, perhaps} a small number of lobbied legislators cannot deliver the votes of their non-lobbied colleagues with certainty. \textbf{One can think of this uncertainty as an additional influence on the legislature's preferences about which all parties---executives, legislators and lobbies alike---are uncertain.}

In this case \textbf{of political uncertainty}, I show that the legislatures disrupt trade agreements with a higher probability and set higher trade war tariffs when lobbying effort increases. Because the lobbies respond to higher trade agreement tariffs by decreasing effort (and therefore the probability the agreement will fail to be ratified or will be broken), the executives must trade off the level of social welfare derived while a trade agreement is in force---since they prefer low tariffs---and the chances that the agreement will remain in force.
